---
title: |
  Jeffco Listens: Family Survey  
  2025-2026
output:
  powerpoint_presentation:
    reference_doc: JeffcoTemplate3.pptx
knit: |
  (function(input, encoding, ...) {
    rmarkdown::render(
      input,
      encoding = encoding,
      output_format = rmarkdown::powerpoint_presentation(
        reference_doc = "JeffcoTemplate3.pptx"
      )
    )

    # ---- Post-process: inject alt text into pptx ----
    alt_store_file <- "_alt_texts.rds"
    if (file.exists(alt_store_file)) {
      message("Injecting alt text into pptx...")
      alt_list   <- readRDS(alt_store_file)
      alt_values <- unname(unlist(alt_list))
      output_file <- sub("\\.Rmd$", ".pptx", input)
      prs <- officer::read_pptx(output_file)
      n_slides <- length(prs)

      img_index <- 1L
      for (i in seq_len(n_slides)) {
        raw_xml <- prs$slide$get_slide(i)$get()
        pics    <- xml2::xml_find_all(raw_xml, ".//*[local-name()='pic']")
        for (pic in pics) {
          if (img_index > length(alt_values)) break
          cNvPr <- xml2::xml_find_first(pic, ".//*[local-name()='cNvPr']")
          if (!is.na(cNvPr)) {
            xml2::xml_set_attr(cNvPr, "descr", alt_values[[img_index]])
            message("  Slide ", i, ": set alt text -> '", alt_values[[img_index]], "'")
            img_index <- img_index + 1L
          }
        }
      }

      print(prs, target = output_file)
      file.remove(alt_store_file)
      message("Done. Alt text patched into: ", output_file)
    }
  })
---

```{r setup, include=FALSE}
library(knitr)

# Global store: chunk_label -> alt_text string
.alt_text_store <- list()

# Chunk hook: after each chunk, grab labs(alt=) from any ggplot
knit_hooks$set(capture_alt = function(before, options, envir) {
  if (!before) {
    p <- tryCatch(get(options$label, envir = envir), error = function(e) NULL)
    if (inherits(p, "ggplot") && !is.null(p$labels$alt)) {
      .alt_text_store[[options$label]] <<- p$labels$alt
      saveRDS(.alt_text_store, "_alt_texts.rds")
    }
  }
})

opts_chunk$set(echo = FALSE, capture_alt = TRUE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Slide with MPG

```{r, echo=FALSE}
my_caption = paste0("Graphic of distribution and mean of\n Miles Per Gallon (MGP).\n Mean: ", round(mean(mtcars$mpg)))
```


```{r mpg, warning=FALSE, message=FALSE, fig.cap=my_caption}
library(tidyverse)

mpg <-
  ggplot(mtcars, aes(mpg)) +
  geom_histogram(bins = 10) +
  geom_vline(aes(xintercept = mean(mpg)), 
             color = "red", linetype = "dashed", linewidth = 1)  +
  labs(alt = paste0("Graphic of distribution and mean of\n Miles Per Gallon (MGP).\n Mean: ", round(mean(mtcars$mpg))), 
       caption = my_caption)

mpg
```

## Slide with Car weights

```{r weight, warning=FALSE, message=FALSE}
library(tidyverse)

weight <-
  ggplot(mtcars, aes(wt)) +
  geom_histogram(bins = 10) +
  geom_vline(aes(xintercept = mean(wt)), 
             color = "red", linetype = "dashed", linewidth = 1)  +
  labs(alt = paste0("Graphic of distribution and mean of\n car weights.\n Mean Weight: ", round(mean(mtcars$wt))))

weight

```
